---
title: "Disaster Relief Project: Part I"
author: "Add your name here"
date: "`r format(Sys.Date(), '%b %d, %Y')`"
output:
  html_document:
    number_sections: true    
    toc: true
    toc_float: true
    theme: cosmo
    highlight: espresso    
# You can make the format personal - this will get you started:  
# https://bookdown.org/yihui/rmarkdown/html-document.html#appearance_and_style    
---

<!--- Below are global settings for knitr. You can override any of them by adding the changes to individual chunks --->

```{r global_options, include=FALSE}
knitr::opts_chunk$set(error=TRUE,        # Keep compiling upon error
                      collapse=FALSE,    # collapse by default
                      echo=TRUE,         # echo code by default
                      comment = "#>",    # change comment character
                      fig.width = 5.5,     # set figure width
                      fig.align = "center",# set figure position
                      out.width = "49%", # set width of displayed images
                      warning=TRUE,      # show R warnings
                      message=TRUE)      # show R messages
```

<!--- Change font sizes (or other css modifications) --->
<style>
h1.title {
  font-size: 2.2em; /* Title font size */
}
h1 {
  font-size: 2em;   /* Header 1 font size */
}
h2 {
  font-size: 1.5em;
}
h3 { 
  font-size: 1.2em;
}
pre {
  font-size: 0.8em;  /* Code and R output font size */
}
</style>



**SYS 6018 | Spring 2021 | University of Virginia **

*******************************************

# Introduction 

Tell the reader what this project is about. Motivation. 

# Training Data / EDA

Load data, explore data, etc. 

```{r load-packages, warning=FALSE, message=FALSE}
# Load Required Packages
library(tidyverse)
```


# Model Training

## Set-up 

## Logistic Regression

## LDA

## QDA

## KNN

### Tuning Parameter $k$

How were tuning parameter(s) selected? What value is used? Plots/Tables/etc.

## Penalized Logistic Regression (ElasticNet)

### Tuning Parameters

**NOTE: PART II same as above plus add Random Forest and SVM to Model Training.**

## Threshold Selection


# Results (Cross-Validation)

** CV Performance Table Here**


# Conclusions

### Conclusion \#1 

### Conclusion \#2

### Conclusion \#3


```{r, echo=FALSE}
# knitr::knit_exit()    # ignore everything after this
## Uncomment this line for Part I
## You can remove the entire code chunk for Part II
```


# Hold-out Data / EDA

Load data, explore data, etc. 


# Results (Hold-Out)

**Hold-Out Performance Table Here**


# Final Conclusions

### Conclusion \#1 

### Conclusion \#2

### Conclusion \#3

### Conclusion \#4 

### Conclusion \#5

### Conclusion \#6

